---
title: "High Intensity Users - Dummy Dataset"
author: "DPT Informatics"
date: "13/09/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
library(dplyr)
library(wakefield)
library(openxlsx)
library(stringr)
library(lubridate)


```



SELECT ClientID, COUNT(*) AS [Number of Referrals in Last 6 Months],
sum(COUNT(*)) over(order by COUNT(*) DESC rows unbounded preceding) as runningtotal
FROM *table*
WHERE Date >= DATEADD(month, -6, GETDATE())
GROUP BY ClientID
ORDER BY COUNT(*) DESC


```{r}
# ClientID
# [Number of Referrals in Last 6 Months]
# runningtotal

attendances_per_client_df <- wakefield::r_data_frame(n = 472,
  ClientID = wakefield::id(),
  `Number of Referrals in Last 6 Months` = rlnorm(meanlog=2, sdlog=1.2)
  ) %>% 
  mutate(`Number of Referrals in Last 6 Months` = ceiling(`Number of Referrals in Last 6 Months`)) %>% 
  arrange(desc(`Number of Referrals in Last 6 Months`)) %>% 
  mutate(runningtotal = cumsum(`Number of Referrals in Last 6 Months`)) %>% 
  mutate(ClientID = glue::glue("1000{ClientID}"))

attendances_per_client_df %>%
  write.xlsx(file="attendances_per_client_dummy_data.xlsx")

```


```{r}
high_intensity_users <- attendances_per_client_df %>% 
  slice_head(n=30) %>%
  select(-runningtotal) %>% 
  rename(`FRS Calls in Last 12 Months` = `Number of Referrals in Last 6 Months`)

high_intensity_users %>% 
  write.xlsx("high_intensity_users_dummy_data.xlsx")

client_ids <- high_intensity_users %>% select(ClientID) %>% pull()
```

# Begin by creating dataset for type of interest (in this case FRS) thaat will match the specified number of calls

```{r}
list_frs_dfs <- list()

for (client in (1:length(client_ids))) {
 
  client_row <- high_intensity_users[client,]
  
  this_client_id <- client_row %>% select(ClientID) %>% pull() %>% as.character()
  
  n <- client_row %>% select(`FRS Calls in Last 12 Months`) %>% pull()
  
  list_frs_dfs[[client]] <-   wakefield::r_data_frame(
    n = n,
    ClientID = this_client_id,
    Type = "Crisis Line Call",
    Label = "Crisis Line Call",
    Date = wakefield::dob(start=Sys.Date() - 365 * 7, k = 365 * 7),
    Time = wakefield::time_stamp(random=TRUE, x=seq(0, 23, by = 0.1)),
    Triage = wakefield::r_sample_factor(c("A - Emergency", "B - 4 Hour Response", "C - 24 Hour Response", "D - 48 Hour Response", "E - Requires Specialist Mental Health Assessment but Stable", "F - Not requiring face to face response, specify ongoing support", "G - Advice or information only"), 
                                        prob=c(0.02, 0.04, 0.05, 0.07, 0.15, 0.25, 0.42))
  ) 
  
}

frs <- bind_rows(list_frs_dfs) %>% 
  mutate(EndDate = NULL) %>% 
  mutate(`Additional Tooltip` = glue::glue("Initial Triage Rating: {Triage} </br> Call Time: {substr(Time, 1, 5)}")) %>%
  select(-c(Time, Triage))
```
### Create list of place of safety attendances

```{r}
list_pos_dfs <- list()

for (client in (1:length(client_ids))) {
 
  client_row <- high_intensity_users[client,]
  
  this_client_id <- client_row %>% select(ClientID) %>% pull() %>% as.character()
  
  n <- (rnorm(n=1, mean=7, sd=20) %>% round(0) %>% abs()) + 1
  
  list_pos_dfs[[client]] <-   wakefield::r_data_frame(
    n = n,
    ClientID = this_client_id,
    Type = "Place of Safety (POS)",
    Label = "Place of Safety (POS)",
    Date = wakefield::dob(start=Sys.Date() - 365 * 7, k = 365 * 7),
    Time = wakefield::time_stamp(random=TRUE, x=seq(0, 23, by = 0.1)),
    Transport = wakefield::r_sample_factor(c("Ambulance", "Police", "Other", "Not Recorded"), 
                                        prob=c(0.1, 0.6, 0.2, 0.1))
  ) 
  
}

pos <- bind_rows(list_pos_dfs) %>% 
  mutate(EndDate = NULL) %>% 
  mutate(`Additional Tooltip` = glue::glue("Arrival Method: {Transport} </br> Arrival Time: {substr(Time, 1, 5)}")) %>%
  select(-c(Time, Transport)) 
```


### Create list of liaison psychiatry attendances

```{r}
list_liaison_dfs <- list()

for (client in (1:length(client_ids))) {
 
  client_row <- high_intensity_users[client,]
  
  this_client_id <- client_row %>% select(ClientID) %>% pull() %>% as.character()
  
  n <- (rnorm(n=1, mean=7, sd=20) %>% round(0) %>% abs()) + 1
  
  list_liaison_dfs[[client]] <-   wakefield::r_data_frame(
    n = n,
    ClientID = this_client_id,
    Type = "Liaison Psychiatry",
    Label = "Liaison Psychiatry",
    Date = wakefield::dob(start=Sys.Date() - 365 * 7, k = 365 * 7),
    Time = wakefield::time_stamp(random=TRUE, x=seq(0, 23, by = 0.1)),
    Location = wakefield::r_sample_factor(c("AMU", "ED", "DGH", "Other"), 
                                        prob=c(0.1, 0.8, 0.1, 0.1))
  ) 
  
}

liaison <- bind_rows(list_liaison_dfs) %>% 
  mutate(EndDate = NULL) %>% 
  mutate(`Response Time Target` = case_when(Location == "ED" | Location == "AMU" ~ "1 hour", TRUE ~ "24 hours")) %>% 
  rowwise() %>% 
  mutate(`Response Time` = case_when(`Response Time Target` == "1 hour" ~ rnorm(1, 80, 13), TRUE ~ (rnorm(1, 1440, 140))/24)) %>% 
  ungroup() %>% 
  mutate(`Response Time` = `Response Time` %>% round(0)) %>% 
  mutate(`Response Time` = case_when(`Response Time Target` == "1 hour" ~ paste(`Response Time`, "minutes"), TRUE ~ paste(`Response Time`, "hours"))) %>% 
  mutate(`Additional Tooltip` = glue::glue("Client Location: {Location} </br>Arrival Time: {substr(Time, 1, 5)}</br>Response Time: {`Response Time`} (target: {`Response Time Target`})")) %>%
  select(-c(Time, Location, `Response Time Target`, `Response Time`))
```


### Next create a list of referrals for these clients

```{r}
list_referral_dfs <- list()

for (client in (1:length(client_ids))) {
 
  client_row <- high_intensity_users[client,]
  
  this_client_id <- client_row %>% select(ClientID) %>% pull() %>% as.character()
  
  n <- (rnorm(n=1, mean=9, sd=5) %>% round(0) %>% abs()) + 1
  
  list_referral_dfs[[client]] <-   wakefield::r_data_frame(
    n = n,
    ClientID = this_client_id,
    Type = "Referral",
    Label = wakefield::r_sample_factor(c("Core Adult Mental Health Team", 
                                         "Crisis Home Treatment Team", 
                                         "Psychology", 
                                         "Support Into Employment", 
                                         "Personality Disorders", 
                                         "Adult ADHD", 
                                         "Adult Autistic Spectrum Service", 
                                         "Mental Health Assessment Team", 
                                         "STEP Team"),
                                       prob=c(0.5, 0.2, 0.1, 0.05, 0.05, 0.05, 0.02, 0.02, 0.01 )),
    Date = wakefield::dob(start=Sys.Date() - 365 * 7, k = 365 * 7),
    ReferralLengthDays = wakefield::normal(365, 365), 
    Reason = wakefield::r_sample_factor(c("Anxiety", "Depression", "Personality Disorders"), prob=c(0.45, 0.45, 0.1))
  ) 
  
}

referrals <- bind_rows(list_referral_dfs) %>% 
  rowwise() %>% 
  mutate(ReferralLengthDays = case_when(Label == "Crisis Home Treatment Team" ~ rnorm(1, 12, 3), TRUE ~ ReferralLengthDays )) %>% 
  ungroup() %>%
  # Order each client's referrals to a particular team by the order in which they tool place
  group_by(ClientID, Label) %>%
  arrange(ClientID, Label, Date) %>% 
  mutate(RowNumber = row_number()) %>% 
  mutate(EndDate = Date + abs(ReferralLengthDays)) %>% 
  mutate(Date = case_when(RowNumber > 1 ~ as.Date(NA), TRUE ~ Date),
         EndDate = case_when(RowNumber > 1 ~ as.Date(NA), TRUE ~ EndDate)) %>% 
  
  mutate(Date = case_when(RowNumber == 2 ~ lag(EndDate, 1) + abs(rnorm(1, 365, 120)), TRUE ~ Date) ) %>% 
  mutate(EndDate = Date + abs(ReferralLengthDays)) %>%
  
  mutate(Date = case_when(RowNumber == 3 ~ lag(EndDate, 1) + abs(rnorm(1, 365, 120)), TRUE ~ Date) ) %>% 
  mutate(EndDate = Date + abs(ReferralLengthDays)) %>%
  
  mutate(Date = case_when(RowNumber == 4 ~ lag(EndDate, 1) + abs(rnorm(1, 365, 120)), TRUE ~ Date) ) %>% 
  mutate(EndDate = Date + abs(ReferralLengthDays)) %>% 
  
  ungroup() %>% 
  filter(RowNumber <= 4) %>%
  filter(Date <= Sys.Date()) %>%
  mutate(EndDate = case_when(EndDate > Sys.Date() ~ as.Date(NA), TRUE ~ EndDate)) %>%
  mutate(Reason = case_when(Label == "Crisis Home Treatment Team" ~ "Mental Health Crisis",
                            Label == "STEP Team" ~ "First Episode Psychosis",
                            Label == "Adult ADHD" & RowNumber == 1 ~ "ADHD Diagnosis",
                            Label == "Adult ADHD" & RowNumber > 1 ~ "ADHD Support",
                            Label == "Adult Autistic Spectrum Service" & RowNumber == 1 ~ "ASC Diagnosis",
                            Label == "Adult Autistic Spectrum Service" & RowNumber > 1 ~ "ASC Support",
                            TRUE ~ as.character(Reason))
         ) %>%
  mutate(`Additional Tooltip` = glue::glue("Reason: {Reason}")) %>%
  select(-c(Reason, RowNumber))

```




### Create individual contacts that took place

```{r}
contacts_df_lists <- list()

for (row in 1:nrow(referrals)) {
  
  client_row <- referrals[row,]
  
  this_client_id <- client_row %>% select(ClientID) %>% pull() %>% as.character()
  
  n_contacts <- (rnorm(n=1, mean=12, sd=15) %>% round(0) %>% abs())
  
  if (n_contacts > 1) {

  contacts_df_lists[[row]] <-   wakefield::r_data_frame(
    n = n_contacts,
    ClientID = this_client_id,
    Type = "Contact",
    Label = client_row %>% select(Label) %>% pull() %>% as.character(),
    Date = wakefield::dob(start =  client_row %>% select(Date) %>% pull(), 
                          k = client_row %>% select(ReferralLengthDays) %>% pull() %>% abs()),
    ReferralLengthDays = wakefield::normal(365, 365), 
    ContactMedium = wakefield::r_sample_factor(c("Face to Face", 
                                         "Telephone", 
                                         "Video Call", 
                                         "Text Message", 
                                         "Online Chat", 
                                         "Other"),
                                       prob=c(0.5, 0.2, 0.15, 0.05, 0.05, 0.05)),
    Attended = wakefield::r_sample_factor(c("Attended on Time",
                                            "Attended Late but Seen",
                                            "Attended Late - Not Possible to See",
                                            "Did not Attend"),
                                       prob=c(0.7, 0.1, 0.1, 0.1))
  )
      
  }
}

contacts <- bind_rows(contacts_df_lists) %>%
  mutate(`Additional Tooltip` = glue::glue("Contact Medium: {ContactMedium} </br>{Attended}")) %>% 
  select(-c(Attended, ContactMedium, ReferralLengthDays) )
```

```{r}
referrals <- referrals %>% 
  select(-ReferralLengthDays)
```

### Create ward stays

```{r}
list_inpatient_dfs <- list()

for (client in (1:length(client_ids))) {
 
  client_row <- high_intensity_users[client,]
  
  this_client_id <- client_row %>% select(ClientID) %>% pull() %>% as.character()
  
  n <- (rnorm(n=1, mean=2, sd=1) %>% round(0) %>% abs()) + 1
  
  list_inpatient_dfs[[client]] <-   wakefield::r_data_frame(
    n = n,
    ClientID = this_client_id,
    Type = "Inpatient",
    Label = wakefield::r_sample_factor(c("Zinc Ward", 
                                         "Copper Ward", 
                                         "Titanium House", 
                                         "Magnesium Heights", 
                                         "Tin Ward", 
                                         "Steel House", 
                                         "Strontium View", 
                                         "Cobalt Ward", 
                                         "Beryllium Crisis House")#,
                                       #prob=c(0.5, 0.2, 0.1, 0.05, 0.05, 0.05, 0.02, 0.02, 0.01 )
                                       )
    ,
    Date = wakefield::dob(start=Sys.Date() - 365 * 7, k = 365 * 7),
    StayLengthDays = wakefield::normal(30, 120)#, 
    #Reason = wakefield::r_sample_factor(c("Anxiety", "Depression", "Personality Disorders"), prob=c(0.45, 0.45, 0.1))
  ) 
  
}

inpatient_stays <- bind_rows(list_inpatient_dfs) %>% 
  rowwise() %>% 
  mutate(StayLengthDays = case_when(Label == "Beryllium Crisis House" ~ rnorm(1, 12, 3), TRUE ~ StayLengthDays )) %>% 
  ungroup() %>%
  # Order each client's referrals to a particular team by the order in which they tool place
  group_by(ClientID) %>%
  arrange(ClientID, Date) %>% 
  mutate(RowNumber = row_number()) %>% 
  mutate(EndDate = Date + abs(StayLengthDays)) %>% 
  mutate(Date = case_when(RowNumber > 1 ~ as.Date(NA), TRUE ~ Date),
         EndDate = case_when(RowNumber > 1 ~ as.Date(NA), TRUE ~ EndDate)) %>% 
  
  mutate(Date = case_when(RowNumber == 2 ~ lag(EndDate, 1) + abs(rnorm(1, 30, 120)), TRUE ~ Date) ) %>% 
  mutate(EndDate = Date + abs(StayLengthDays)) %>%
  
  mutate(Date = case_when(RowNumber == 3 ~ lag(EndDate, 1) + abs(rnorm(1, 30, 120)), TRUE ~ Date) ) %>% 
  mutate(EndDate = Date + abs(StayLengthDays)) %>%
  
  mutate(Date = case_when(RowNumber == 4 ~ lag(EndDate, 1) + abs(rnorm(1, 30, 120)), TRUE ~ Date) ) %>% 
  mutate(EndDate = Date + abs(StayLengthDays)) %>% 
  
  ungroup() %>% 
  filter(RowNumber <= 4) %>%
  filter(Date <= Sys.Date()) %>%
  mutate(EndDate = case_when(EndDate > Sys.Date() ~ as.Date(NA), TRUE ~ EndDate)) %>%
  mutate(`Additional Tooltip` = "") %>%
  select(-c(RowNumber, StayLengthDays))

```

```{r}
inpatient_stays %>% 
  rename(AdmissionDate = Date,
         DischargeDate = EndDate,
         Specialty = Type,
         Ward = Label) %>%
  write.xlsx("inpatient_dummy_data.xlsx")
```


### Write to file


```{r}
referrals %>% 
  union_all(contacts) %>% 
  union_all(frs) %>% 
  union_all(pos) %>% 
  union_all(liaison) %>% 
  union_all(inpatient_stays) %>% 
  write.xlsx("community_simplified_dummy_data.xlsx")
```

```{r}
print("done")
```


